Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-05-07 Tex/elsevier/trindade_solar_energy_rev0.tex
updated text

\section*{List of Abbreviations, Units and Nomenclature}
\noindent $a$ Ideality or quality factor \\
AC Alternating current \\
$C_{10}$ 10h of rated battery capacity \\
$C_{bank}$ Total capacity of the battery bank \\
CBMC C Bounded Model Checker \\
$ cos \varphi $ Power factor of the inverter \\
CPA Configurable Program Analysis \\
CPAchecker Configurable Program Analysis Checker \\
DC Direct current \\
$DOD$ Depth of discharge ($DOC=1-SOC$) \\
$E_{consumption}$ Energy consumption \\
$E_{corrected}$ Energy corrected \\
$E_{p}$ Energy produced by one panel \\
ESBMC Efficient SMT-based Bounded Model Checker \\
$G$ Solar irradiance \\
$ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$) \\
$I$ Current \\
$I_{0}$ Reverse saturation current \\
$ I_{AC} $ Current that the inverter supply to the house \\
$I_{c,min}$ Charge controller minimum current \\
$ I_{DC} $ Current required by the inverter from the DC source \\
$ I_{in} $ Input current \\
$I_{load}$ Current that feed the load \\
$ I_{out} $ Output current \\
$I_{ph}$ Photocurrent \\
$ I_{ph,ref} $ Photocurrent at STC \\
$I_{pv}$ Current from the PV system \\
$ I_{sc} $ Short-circuit current \\
$ I_{sc,amb} $ Ambient short-circuit current \\
$ I_{sc,ref} $ Short-circuit current at STC \\
$ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); \\
$MAX_{AC,ref}$ Peak power that the inverter can support \\
$N$ Number of series-connected cells \\
$N_{B}total$ Sized number of batteries \\
$N_{BP}$ Sized number of parallel batteries \\
$N_{BP}min$ Total minimum number of parallel batteries \\
$N_{BS}$ Sized number of series batteries \\
$N_{BS}min$ Total minimum number of series batteries \\
NOCT Nominal Operating Cell Temperature \\
$N_{PS}$ Sized number of panels in series \\
$N_{PSmin}$ Total number of panels in series \\
$N_{PP}$ Sized number of panels in parallel \\
$N_{PPmin}$ Total umber of panels in parallel \\
$ N_{TP} $ Sized number of panels \\
$N_{TPmin}$ Total minimum number of needed solar panels \\
PV Photovoltaic \\
P Power \\
$P_{in}$ Input power \\
$P_{out}$ Output power \\
$P_{surge}$ Maximum peak power demanded by house for few seconds \\
$q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $) \\
SAT Satisfiability or Boolean satisfiability problem \\
SAT When returns a failure from the verification tool \\
SMT Satisfiability modulo theories \\
$ SOC $ Battery state of charge \\
STC Standard Test Condition (reference state) \\
$T$ Temperature \\
$ T_{air} $ Ambient temperature \\
$ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$) \\
UNSAT Condition when verification tool succeeds (could not reach an error) \\
V Voltage \\
$ V_{AC}  $ Voltage that the inverter supply to the house \\
$V_{c}$ Battery charge voltage  \\
$V_{d}$ Battery discharge voltage \\
$ V_{DC} $ Input voltage to the inverter delivered by the DC source \\
$ V_{in} $ Input voltage \\
$ V_{oc} $ Open-circuit voltage \\
$ V_{oc,ref} $ Reference open-circuit voltage at STC \\
$ V_{out} $ Output voltage \\
$ V_{system} $ DC voltage of the bus \\
$V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $) \\
$\Delta T$ Temperature variation ($\Delta T=T-T_{ref} $) \\
$ \mu_{I} $ Short-circuit current temperature coefficient ($A/K$) \\
$ \mu_{V} $ Open-circuit voltage temperature coefficient ($ V/K $) \\
$\eta_{b}$ Battery efficiency \\
$\eta_{c}$ Charge controller efficiency \\
$\eta_{i}$ Inverter efficiency \\
$\eta_{p}$ PV panel efficiency \\

%\linenumbers

@@

The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 

@@

Therefore this is a additional feature included at this paper. The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to worst monthly average solar energy~\cite{Pinho}. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

@@

Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

>>>>

@@

The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 

@@

Therefore this is a additional feature included at this paper. The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

@@

Related to the charge controller, here the model with MPPT is adopted and initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}
